Feature Selection and Classification of \\ Spam on Social Networking Sites

### 2012-05-09 docs/paper/paper.tex
update

\title{Detecting Spam on Social Networking Sites}

@@

\maketitle
\begin{abstract}
Social networking sites (SNSs) see a variety of spam and scams targeted at 
their users. In contrast to the more limited amounts of secondary information 
available when analyzing email spam, spam on SNSs is accompanied by a wealth 
of data on the sender, which can be used to build more accurate detection mechanisms. 
We analyze public and private data from a popular social network in order to 
gain insight into the various features spam messages and the accompanying user 
accounts and profiles available to site operators. By examining the ....
\end{abstract}

@@

Social networks of any significant size see constant spam, scams
and phishing attacks. The nature of these attacks can be quite diverse
and difficult detect. Marketers can spam members with unwanted
advertisements, fraudsters lure users with advance fee frauds and
other confidence tricks, while others may attempt to steal user
information by directing users to external phishing pages. 
Sites with global reach see communication among its members in a 
number foreign languages with varying levels
of ability. This means that much benign content shares characteristics
like misspellings, awkward phrases, etc. that might have made certain
types of common frauds and spam more easy to distinguish on US-based
(or English-language) sites.
% focus on extra impact of non-public features vs. public (bag-of-words)

@@

Email spam and techniques with which to combat it has been studied 
extensively. Like
This paper examines in detail the types of malicious and benign
content that are encountered on social networks by analyzing
experimental data available from InterPals, an international social network
for cultural exchange and language practice. For example, the site
attracts a wide variety of financial scams, ranging from Nigerian
``419" scams to romance scams. Another prevalent problem is spam with
links to third-party websites, directing users to various porn/webcam
sites, phishing sites or various untrustworthy online marketplaces.

@@

\textbf{Advance Fee Fraud} We observed this scam to come in various flavors.  (inheritance, lottery,  etc)
\textbf{Romance Scams:} These 
\textbf{Sexual Solicitation}
\textbf{Porn Ads}
\textbf{Advertising External Sites}
\textbf{Webcam Ads}
\textbf{Money Muling}
\textbf{Begging \& Gift Requests}
\textbf{Business Proposals}

This categorizations are based only on observation. Analyzing the relevant terms in log comments entered by moderators when deleting spammer accounts provides the following breakdown:

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Analysis}
% Vern wants site owner perspective on how to apply classifiers
From a site's perspective, ...

- plan to implement SVM, despite speed tradeoff

@@

Another direction for future research would be to examine data other than messages. We have access to millions 
of wall posts and photo comments, making it possible to investigate the characteristics of spam in these genres. 
Wall posts and comments tend to be comparatively short, so we might

@@

As a part of this project, we performed some qualitative analysis on spam and differentiated between 
some major categories of undesirable messages that we observed on the InterPals web site. However, we would 
like to gain a better understanding of the relative volume of each type of scam

Characteristics of spam messages vary widely depending on the type of spam
we currently lump all spam into a single category; we plan to build on the classes we mentioned in section()
We are currently in the process of extending the moderation interface to include more specific tagging capabilities
%- certain classifiers might work better on certain types of spam
%- clustering to see how well these classes fit the spam types on the site

@@

It is also anecdotally clear from moderator log messages that spammers re-use their profile photos and 
these photos are often of celebrities or simply stock photos. Hashing these images

Server access logs, search logs and user viewing histories from InterPals, all of which are available to us, offer another avenue for future research. It is conceivable that certain spammers may have similar site usage patterns, in terms of HTTP request intervals,

\subsection{Testing \& Evaluation}

- test SVM and other classifiers on newer data
-

>>>>

\title{Feature Selection and Classification of \\
    Spam on Social Networking Sites}

@@

\maketitle
\begin{abstract}
Social networking sites (SNSs) see a variety of spam and scams targeted at 
their users. In contrast to the more limited amounts of secondary information 
available when analyzing email spam, spam on SNSs is accompanied by a wealth 
of data on the sender, which can be used to build more accurate detection mechanisms. 
We analyze 4 million private messages as well as other public and private data from 
a popular social network in order to gain insight into the various features of 
spam messages and the accompanying user accounts data available to site operators. 
We use these insights to choose features that best differentiate spammers from 
legitimate, ``ham," users.  Finally, we extract these features from the site's data 
and use them to train and evaluate classifiers.
\end{abstract}

@@

Social networks of any significant size see a constant stream of spam, scams and phishing attacks. 
The nature of this unwanted activity can be quite diverse, specific to a site's target audience and 
often not trivial to detect. Marketers can spam members with unwanted advertisements, fraudsters 
lure users with advance fee frauds and other confidence tricks, while others may attempt to steal user
information by directing users to external phishing pages. In contrast to email spam, social spam 
has a more personal component, since both spammers and legitimate users (``ham" users) have accompanying 
profiles with descriptive information.

Sites with global reach see communication among its members in a number foreign languages with 
varying levels of ability. This means that much benign content shares characteristics like misspellings, 
awkward phrases, etc. that might have made certain types of common frauds and spam more easy to 
distinguish on US-based (or English-language) sites.

Recent research has begun to evaluate Email spam and techniques with which to combat it has been studied 
extensively. Like

% focus on extra impact of non-public features vs. public (bag-of-words)

@@

This paper examines in detail the types of malicious and benign
content that are encountered on social networks by analyzing
experimental data available from InterPals, an international social network
for cultural exchange and language practice. For example, the site
attracts a wide variety of financial scams, ranging from Nigerian
``419" scams to romance scams. Another prevalent problem is spam with
links to third-party websites, directing users to various porn/webcam
sites, phishing sites or various untrustworthy online marketplaces.

@@

\begin{itemize}
\item \textbf{Advance Fee Fraud} We observed this scam to come in various flavors.  (inheritance, lottery,  etc)
\item \textbf{Romance Scams:} These 
\item \textbf{Sexual Solicitation}
\item \textbf{Porn Ads}
\item \textbf{Advertising External Sites}
\item \textbf{Webcam Ads}
\item \textbf{Money Muling}
\item \textbf{Begging \& Gift Requests}
\item \textbf{Business Proposals}
\end{itemize}

These categorizations are based only on cursory manual observation of a sample of several tens of thousands 
spam-labeled messages. We plan to quantify the volume of messages in each of these categories and 
attempt to provide a finer granularity of categorization in future research.

%Analyzing the relevant terms in log comments entered by moderators when 
%deleting spammer accounts provides the following breakdown:

@@

@@

Another direction for future research would be to examine data other than messages. We have access to millions 
of wall posts and photo comments, making it possible to investigate the characteristics of spam in these genres. 
Wall posts and comments tend to be comparatively short, which should present a slightly different classification 
problem.

We have also recently observed spammers attacking the report system by reporting large numbers of legitimate users 
with complaints consisting of nonsensical text or form messages. In addition to offering another application for 
classifiers, the data we are collecting should offer a window into the retaliatory techniques of miscreants on 
SNSs.

@@

As a part of this project, we performed some qualitative analysis on spam and differentiated between 
some major categories of undesirable messages that we observed on the InterPals web site. However, we would 
like to gain a better understanding of the relative volume of each type of scam. To this end, we plan to 
experiment with clustering algorithms to attempt to identify and quantify subclasses of spam.

Furthermore, characteristics of spam messages vary substantially depending on the type of spam or scam in question. 
The classifiers that we trained and evaluated in this project all spam messages as a single category. We are currently 
investigating multiclass classifiers as a potential tool to identify the type of 
spam in question with greater precision. Specifically, we are considering multiclass SVMs, which reduce 
multiclass problems into multiple binary classification problems.\cite{duan}

From a site's perspective, this finer granularity is desirable not only 
because specialty classifiers could be trained to recognize specific classes of spam, but also in order to 
trigger different courses of action (\eg automatic account deletion, warning messages, reports to human moderators) 
based on the class and probability of spam detected.

We are currently extending the moderation interface to include more specific tagging capabilities, which should aid 
in generating labels for multiclass classifiers and for seeding semi-supervised clustering algorithms (see Basu et al. 
\cite{basu}).

@@

It is also anecdotally clear from moderator log messages that spammers re-use their profile photos and 
these photos are often of celebrities or simply stock photos. Fingerprinting and perceptual hash techniques 
such as Marr wavelet, discrete cosine transform (DCT), color histograms, etc., which provided by the 
pHash library, \footnote{http://www.phash.org} seem to promising in detecting image re-use.

Server access logs, search logs and user viewing histories from InterPals, all of which 
are available to us, offer another avenue for future research. It is conceivable that certain 
spammers may have similar site usage patterns, in terms of HTTP request intervals, search queries, 
and so on, which might prove useful in their detection.

\subsection{Site Implementation}

Given the promising results of SVM classifiers in this project, we plan to test and implement a classifier that will 
be integrated into the site application code itself. Initially, we envision this as a system that automatically flags 
potential spam messages and brings them to the attention of human moderators. Moderators will then be able to manually 
make a decision as to whether the messages are spam or not. In order to diminish the effect of subjectivity or moderator 
error, each message will be vetted by several moderators, and the majority decision will be accepted as ground ``truth." 
Recording these messages and moderator decision will allow us to further evaluate the performance of these classifiers in 
the ``wild."
